Correlation of filter methods

### 2019-06-27 analysis/filter-correlation.Rmd
add new report
wflow_publish(knitr_in("analysis/filter-correlation.Rmd"), view = FALSE)

  fv_nri_info.gain5, fv_nri_info.gain10,
  fv_nri_info.gain15, fv_nri_info.gain20,
  fv_nri_info.gain25, fv_nri_info.gain30
)
```

@@

Spearman's rank correlation is used since we compare rankings against each other.

@@

```{r eda-20}
# combine filter values

>>>>

  fv_nri_info.gain5, fv_nri_info.gain10,
  fv_nri_info.gain15, fv_nri_info.gain20,
  fv_nri_info.gain25, fv_nri_info.gain30
)
library("rgdal")
```

@@

Spearman's rank correlation is used because we compare rankings against each other.

@@

```{r eda-20, warning=FALSE}
# combine filter values
